Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
figures in article

	\begin{tabular}{@{}lrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=16$}\\
      \cmidrule(r){2-7}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      5706 & 2 & 28 & 90 & 2120 & 1780\\
      %Time (in ms) &
      %826 & 14 & 26 & 252 & 606 & 4801\\
      $L_\infty$ error (\wrt $l_0$) &
      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
      $L_2$ error (\wrt $l_0$) &
      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
      \bottomrule
    \end{tabular}

  \end{center}
  \caption{object, size, radius, full res, num of vertices (timings
    only consider the curvature estimation step).\label{tab:full-res-stat}}
\end{table}

\begin{figure}
  \begin{center}
    \subfigure[]{\framebox{octa $l_4$}}
   \subfigure[]{\framebox{octa $l_3$}}
   \subfigure[]{\framebox{octa $l_2$}}
   \subfigure[]{\framebox{octa $l_1$}}
   \subfigure[]{\framebox{octa $l_0$}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower using mipmap approximation of different levels : $l_4$, $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
  %
  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

      \begin{axis}[
          ybar stacked,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      xxx-R1, xxx-R2},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000)
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (xxx-R1,1) (xxx-R2,1)};
        %l4
        \addplot+[ybar] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000)
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (xxx-R1,1) (xxx-R2,1)};
        %l3
        \addplot+[ybar] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (xxx-R1,1) (xxx-R2,1)};
        %l2
        \addplot+[ybar] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000)
          (Snow-R10,13.777000) (Snow-R20,37.700000) (xxx-R1,1) (xxx-R2,1)};
        %l1
        \addplot+[ybar] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000)
          (Snow-R10,39.627000) (Snow-R20,217.954000) (xxx-R1,1) (xxx-R2,1)};
        %l0
        \addplot+[ybar] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000)
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (xxx-R1,1) (xxx-R2,1)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}

      \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      xxx-R1, xxx-R2},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000)
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (xxx-R1,1) (xxx-R2,1)};
        %Hierarchical measurement
        \addplot+[ybar] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000)
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (xxx-R1,1) (xxx-R2,1)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}

>>>>

	\begin{tabular}{@{}lrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=16$}\\
      \cmidrule(r){2-7}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      5706 & 2 & 28 & 90 & 2120 & 17080\\
      %Time (in ms) &
      %826 & 14 & 26 & 252 & 606 & 4801\\
      $L_\infty$ error (\wrt $l_0$) &
      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
      $L_2$ error (\wrt $l_0$) &
      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
      \bottomrule
    \end{tabular}

  \end{center}
  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on  object, size, radius, full res, num of vertices (timings
    only consider the curvature estimation step).\label{tab:full-res-stat}}
\end{table}

\begin{figure}[!htbp]
  \begin{center}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
  %
  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

      \begin{axis}[
          ybar stacked,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      xxx-R1, xxx-R2},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000)
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (xxx-R1,1) (xxx-R2,1)};
        %l4
        \addplot+[ybar] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000)
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (xxx-R1,1) (xxx-R2,1)};
        %l3
        \addplot+[ybar] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (xxx-R1,1) (xxx-R2,1)};
        %l2
        \addplot+[ybar] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000)
          (Snow-R10,13.777000) (Snow-R20,37.700000) (xxx-R1,1) (xxx-R2,1)};
        %l1
        \addplot+[ybar] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000)
          (Snow-R10,39.627000) (Snow-R20,217.954000) (xxx-R1,1) (xxx-R2,1)};
        %l0
        \addplot+[ybar] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000)
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (xxx-R1,1) (xxx-R2,1)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}
%
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      xxx-R1, xxx-R2},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000)
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (xxx-R1,1) (xxx-R2,1)};
        %Hierarchical measurement
        \addplot+[ybar] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000)
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (xxx-R1,1) (xxx-R2,1)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
